Covariance

### 2019-03-07 draft/paper.tex
script for theory power spectra

\title[Covariance]{Covariance}
\author[Carlos Garc\`{i}a Garc\`{i}a]{Carlos Garc\`{i}a Garc\`{i}a$^1$\thanks{carlosgarcia@iff.csic.es}\\
$^{1}$Oxford Astrophysics, Department of Physics, Keble Road, Oxford, OX1 3RH, UK
}

@@

\section{Analytical Covariance}
\begin{itemize}
\item Naive Covariance
\item Approximation 1
\item Approximation 2
\end{itemize}

>>>>

\title[Covariance]{Covariance}
\author[C. Garc\'{i}a Garc\'{i}a et al.]{Carlos Garc\'{i}a Garc\'{i}a$^1$\thanks{carlosgarcia@iff.csic.es}, David Alonso$^2$\thanks{david.alonso@physics.ox.ac.uk}, Emilio Bellini$^2$\thanks{emilio.bellini@physics.ox.ac.uk}\\
$^{1}$IFF\\
$^{2}$Oxford Astrophysics, Department of Physics, Keble Road, Oxford, OX1 3RH, UK
}

@@

\section{Analytical Covariance}
This section presents the analytical calculation of the pseudo-$C_\ell$ covariance. The treatment and approximations used are similar to those presented in \todo{cite} for spin-0 quantities, in \todo{cite} for particular spin-0 and spin-2 correlations and in \todo{cite} for the 3D density field. We reproduce the formalism here in order to provide a complete set of formulas applicable to any cross-correlation in both curved and flat skies.

\begin{itemize}
\item Naive Covariance
\item Approximation 1
\item Approximation 2
\end{itemize}
